\documentclass[a4paper,11pt]{article}

% Package imports
\usepackage{xcolor}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{fontawesome5}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}

% Page layout
\geometry{left=1.4cm, top=1.2cm, right=1.4cm, bottom=1.2cm}

% Section formatting
\titleformat{\section}
  {\large\scshape\raggedright}{}{0em}{}[\titlerule \vspace{-5pt}]

% Custom commands for entries
\newcommand{\resumeItem}[1]{\item\small{#1}}

\newcommand{\resumeSubheading}[4]{
\vspace{1mm}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & \textit{\footnotesize{#4}} \\
        \textit{\footnotesize{#3}} & \footnotesize{#2}
    \end{tabular*}
    \vspace{-2mm}
}

% Resume Start
\begin{document}

% Header
\begin{center}
    {\huge\textbf{Sneha Sharma}} \\[3mm] % Adjust spacing below name
    
    \small
    \faPhone\ \href{tel:+91 8120752882}{+91 8120752882} \hspace{10pt} % Phone and Email in one line
    \faEnvelope\ \href{mailto:snehasharma08012003@gmail.com}{snehasharma08012003@gmail.com} \\[2mm]

    \faGithub\ \href{https://github.com/iamsnehaa}{iamsnehaa}\hspace{10pt}
    \faLinkedin\ \href{https://www.linkedin.com/in/snehehe/}{snehehe} \hspace{10pt}
    \faTwitter\ \href{https://x.com/snehehee}{snehehee}
\end{center}
\vspace{-3mm}

% Skills Section
\section{\textbf{Skills}}
\small
\textbf{Frontend:} TypeScript, React.js, Next.js, Tailwind CSS \\
\textbf{Backend:} Node.js, Express.js, Prisma \\
\textbf{Database:} MongoDB, PostgreSQL \\
\textbf{Tools:} Git, Docker, Version Control

% Experience Section
\section{\textbf{Experience}}
\begin{itemize}[leftmargin=*, labelsep=1mm]
    \resumeSubheading
        {IBM Skillsbuild(AICTE)}{Remote}
        {\textbf{Data Analytics Intern}}{Jun 2023 – July 2023}
        \resumeItem{Analyzing Dataset and gained knowledge about Data Visualization.}
        \resumeItem{Worked with libraries such as Numpy and Pandas.}

    

    \resumeSubheading
        {Content Head - Microsoft Learn Student Ambassador}{LNCTU}
        {\textbf{Content Writer, Event Host}}{July 2023 – Present}
        \resumeItem{Organized and hosted multiple technical events and workshops.}
        \resumeItem{Created technical content, improving engagement and reach.}
        \resumeItem{Led collaborations and networking initiatives.}
\end{itemize}

% Projects Section
\section{\textbf{Projects}}
\begin{itemize}[leftmargin=*, labelsep=1mm]
    \resumeSubheading
        {Dukaan}{}
        {}{}
        \resumeItem{Ecommerce API for Shopaholics and fashionista's to find variety of clothings at a place.}
        \resumeItem{Tech Stack: React.js, Node.js, Tailwind CSS, Mongo DB}
        

    \resumeSubheading
        {Far from Home (Farm for home)}{}
        {}{}
        \resumeItem{Designed and implemented a website to connect farmers to the consumers directly to avoid intermediaries.}
        \resumeItem{Tech Stack: React.js, Node.js, Tailwind CSS, Mongo DB}

    \resumeSubheading
        {Organza}{}
        {}{}
        \resumeItem{Ecommerce API to provide a variety of organic products for household purposes and to provide fresh veggies and fruits.}
        \resumeItem{Tech Stack: Next,js, Tailwind CSS, PostgreSQL}

     \resumeSubheading
        {Mini Projects}{}
        {}{}
        \resumeItem{The HomePage built through Next.js}
        \resumeItem{Series of mini projects like qr code generator, weather detector,etc.}
        \resumeItem{Tech Stack: HTML, CSS JavaScript (Next.js)}
\end{itemize}

% Education Section
\section{\textbf{Education}}
\begin{itemize}[leftmargin=*, labelsep=1mm]
    \resumeSubheading
        {LNCT University}{Bhopal, India}
        {B.Tech in Computer Science Engineering 
        CGPA: 8.14/10}{2021-2025}
    \resumeSubheading
        {Carmel Convent School}{Gwalior, India}
        {X|XII (CBSE)}{2019|2021}
       
\end{itemize}

\end{document}
